Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-15 paper.tex
snippet style

\colorlet{titlecolor}{SkoleOrange!50!black}
\colorlet{codeblockcolorbase}{SkoleLightBrown!80!black}
\colorlet{codeblockcolor}{codeblockcolorbase!08}

\lstset{language=python,
extendedchars=true,
backgroundcolor=\color{codeblockcolor},
frame=single,
xleftmargin = 0pt,
numbersep = 0pt,
framexleftmargin = 0pt,
resetmargins = true,
framesep = 0pt,
rulesep = 0pt,
basicstyle=\ttfamily\footnotesize,
fillcolor=\color{codeblockcolor},
rulecolor=\color{lightgrey},
aboveskip = 0.5ex,
belowskip = 0.6ex,
escapebegin={\color{darkgreen}},
keywordstyle=\sffamily\color{lightgrey},
identifierstyle=\ttfamily,
commentstyle=\slshape\color{darkgreen},
stringstyle=\ttfamily\color{blue},
showstringspaces=false,
tabsize=2,
%breaklines=true,
morekeywords={{,},=,:}, 
classoffset=0,
}

>>>>

\definecolor{rulecolor}{RGB}{210,210,210}
\colorlet{titlecolor}{SkoleOrange!50!black}
\colorlet{codeblockcolorbase}{SkoleLightBrown!80!black}
\colorlet{codeblockcolor}{codeblockcolorbase!08}

\lstset{language=Python,
extendedchars=true,
backgroundcolor=\color{codeblockcolor},
frame=single,
xleftmargin = 0pt,
numbersep = 0pt,
framexleftmargin = 0pt,
resetmargins = true,
framesep = 0pt,
rulesep = 0pt,
basicstyle=\ttfamily\footnotesize,
fillcolor=\color{codeblockcolor},
rulecolor=\color{rulecolor},
aboveskip = 0.5ex,
belowskip = 0.6ex,
escapebegin={\color{darkgreen}},
keywordstyle=\sffamily\color{darkblue},
identifierstyle=\ttfamily,
commentstyle=\slshape\color{darkgreen},
stringstyle=\ttfamily\color{orange},
showstringspaces=false,
tabsize=2,
%breaklines=true,
morekeywords={{,},=,:},
classoffset=0,
}
